Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-06-16 GWLDCII.tex
tweaked picture in Lem 3.5, added section 5 picture to pictures doc

\bas \begin{tikzpicture}[rotate=15,baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLD{15}{2}
	%\drawnumbers
	%\drawprop{1}{0}{4}{0}
	\begin{scope}
	\clip (0,0) circle (\radius cm);
	\draw[propagator] (\angle*5.3:\radius*1.2cm) to [bend left=50] (\angle*7.7:\radius*1.2cm);
	\node at (\angle*6.5:\radius*0.6cm) {\footnotesize $p_1$};
	\end{scope}
    \drawlabeledprop{3}{0}{10}{0}{\footnotesize \qquad $q_1$}
    \node at (\angle*5:\radius*1.15cm) {\footnotesize $j_1$};
    \node at (\angle*10:\radius*1.15cm) {\footnotesize $i_1$};
	\node at (10:\radius*0.5) {\small $\cP_{in}(q_1)$};
		\end{scope}
	\end{tikzpicture}\eas

Now suppose $q_{r} = (i_r, k_r)$ exists by the induction hypothesis and is oriented $(q_r, <_{i_r})$ so that the previous $p_i$ and $q_i$ are on the outside. For the rest of this proof, we assume this orientation and drop the $<_{i_r}$ from the notation.

>>>>

\bas \begin{tikzpicture}[rotate=15,baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLD{15}{2}
	%\drawnumbers
	%\drawprop{1}{0}{4}{0}
	\begin{scope}
	\clip (0,0) circle (\radius cm);
	\draw[propagator] (\angle*5.3:\radius*1.2cm) to [bend left=50] (\angle*7.7:\radius*1.2cm);
	\node at (\angle*6.5:\radius*0.6cm) {\footnotesize $p_1$};
	\end{scope}
    \drawlabeledprop{3}{0}{10}{0}{\footnotesize \qquad $q_1$};
    \node at (\angle*5:\radius*1.15cm) {\footnotesize $j_1$};
     \node at (\angle*10:\radius*1.15cm) {\footnotesize $i_1$};
     \node at (10:\radius*0.5) {\small $\cP_{in}(q_1)$};
	\node[rotate = 45] at (\angle * 5.2:\radius) {\Large $($};
\node[rotate = -15] at (\angle * 2.7:\radius) {\Large $)$};
\node[rotate = 20] at (\angle* 4:\radius*1.2) {\em \scriptsize 1, 2 or 3 vertices};
		\end{scope}
	\end{tikzpicture}\eas

 %\node[rotate=-15] at (\zero + 2.7*\step:\radius) {\Large $($};
 %    \node[rotate=15] at (\zero + 6.3*\step:\radius) {\Large $)$};
   %  \node at (\zero + 4.5*\step:\radius*0.85) {\em \scriptsize up to 4 vertices here};

\sanote{played with Sian's code. May need to tweak this picture}
Now suppose $q_{r} = (i_r, k_r)$ exists by the induction hypothesis and is oriented $(q_r, <_{i_r})$ so that the previous $p_i$ and $q_i$ are on the outside. For the rest of this proof, we assume this orientation and drop the $<_{i_r}$ from the notation.
